# GithHub + RStudio

[Happy Git and GitHub for the useR](https://happygitwithr.com/) is a great resource for connecting Git/GitHub and RStudio.

[Markdown Cheatsheet](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet)

## Lab Specific Git + RStudio Communication

1. Generate token 

- Log into [https://github.com/](https://github.com/)
- Go to [https://github.com/settings/tokens](https://github.com/settings/tokens)
- Press `Generate new token`
- Select `Generate New Token (Fine-grained, repo-scoped)` from the dropdown menu 
- Create token name 
- No description 
- Select expiration 
- Keep public repositories  
- Don’t add any permissions  
- Click `generate token` 

2. Copy token to computer (notes, word, password organizer, etc…) 

3. Enter GitHub Token into R

- Check if the "gitcreds" package is installed
  - at the prompt in the Console type 'gitcreds()'
    - if an Error is received, please install package
```{r eval = FALSE}    
install.packages("gitcreds")
```

- Add your token to R
  - in the console at the prompt `>` run the command below

```{r eval = FALSE}
gitcreds::gitcreds_set()
```

  - Paste token when prompted 
  
- To check if this worked run "gitcreds::gitcreds_get()"

* also make sure you have packages `rmarkdown` and `knitr` by searching in packages 


## Create a New Project in RStudio from an existing project on GitHub  {-}

Clone Repository



## Create a branch in GitHub  {-}

For each GitHub repository you will be working on in the lab that is shared among others, you will need to create your own Branch. 

Please [create your own branch directly in the repository](https://docs.github.com/en/pull-requests/collaborating-with-pull-requests/proposing-changes-to-your-work-with-pull-requests/creating-and-deleting-branches-within-your-repository) on the GitHub site

## Create Pull Request, for review, on GitHub  {-}